Do we need detailed demographic data to forecast plant population responses to climate change?

### 2015-06-15 manuscript/manuscript.Rmd
updates ms with loyo one step forecasts for IPM

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl

@@

Tables
------
```{r table_1,results='asis',message=FALSE, comment=NA, echo=FALSE}
# Make a table for average residual from each model and year effects structure
ipm_onestep <- readRDS("../montana/ipm/simulations/one_step_results/ipm_one-step_forecasts_combined.rds")
qbm_onestep <- readRDS("../montana/quadBM/simulations/validation_results/qbm_one-step_forecasts_combined.rds")

#IPM
tmpipm <- ddply(ipm_onestep, .(quad, t1, species), summarise,
                mean_pred = mean(cover.t1),
                var_pred = var(cover.t1),
                mean_obs = mean(obs.cover.t1),
                resid = mean(resid),
                quant_dist = quantile(cover.t1*100, probs = 0.95) - quantile(cover.t1, probs = 0.05))
ipmstats <- ddply(tmpipm, .(species), summarise,
                rho = cor(mean_pred, mean_obs),
                mae = mean(abs(resid)),
                var = mean(var_pred),
                mean_cover = mean(mean_obs*100),
                quant_dist = mean(quant_dist))
ipmstats$model <- "IPM"

#QBM
tmpqbm <- ddply(qbm_onestep, .(quad, year, species), summarise,
                mean_pred = mean(predcov),
                var_pred = var(predcov),
                mean_obs = mean(obscov),
                resid = mean(resid),
                quant_dist = quantile(predcov*100, probs = 0.95) - quantile(predcov, probs = 0.05))
qbmstats <- ddply(tmpqbm, .(species), summarise,
                rho = cor(mean_pred, mean_obs),
                mae = mean(abs(resid)),
                var = mean(var_pred),
                mean_cover = mean(mean_obs*100),
                quant_dist = mean(quant_dist))
qbmstats$model <- "QBM"

>>>>

---
layout: 12pt
header-includes:
   - \usepackage{lineno}
   - \linenumbers
   - \usepackage{setspace}
   - \doublespacing
   - \setlength\parindent{24pt}
bibliography: ~/Dropbox/Bibliography/MicroMeso.bib
csl: components/ecology.csl

@@

Tables
------
```{r table_1,results='asis',message=FALSE, comment=NA, echo=FALSE}
####
##  Make a table for average residual from each model and year effects structure
####

##  IPM results
# Read in data
ipm_onestep <- readRDS("../analysis/ipm/simulations/results/one_step_validation/ipm_loyo_forecasts_combined.rds")
# Remove predictions >1 for fair comparison to [0,1] truncated quad model
resets <- which(ipm_onestep[,"cover.t1"]>1)
ipm_onestep[resets, "cover.t1"] <- 1
# Average predictions over quad-year reps
avg_ipm <- ddply(ipm_onestep, .(species, quad, t1), summarise,
                 avg_prediction = median(cover.t1),
                 observation = mean(cover.t0),
                 quant_dist = quantile(cover.t1*100, probs = 0.95) - quantile(cover.t1, probs = 0.05))
# Calculate error
avg_ipm$error <- avg_ipm$observation*100 - avg_ipm$avg_prediction*100
# Aggregate over species
ipmstats <- ddply(avg_ipm, .(species), summarise,
                  mae = mean(abs(error)),
                  mean_cover = mean(observation*100),
                  quant_dist = mean(quant_dist))
ipmstats$model <- "IPM"

##  QBM results
# Read in data
qbm_onestep <- readRDS("../analysis/quadBM/simulations/validation_results/qbm_one-step_forecasts_combined.rds")
# Average predictions over quad-year reps
avg_qbm <- ddply(qbm_onestep, .(species, quad, year), summarise,
                 avg_prediction = median(predcov),
                 observation = mean(obscov),
                 quant_dist = quantile(predcov*100, probs = 0.95) - quantile(predcov, probs = 0.05))
# Calculate error
avg_qbm$error <- avg_qbm$observation*100 - avg_qbm$avg_prediction*100
# Aggregate over species
qbmstats <- ddply(avg_qbm, .(species), summarise,
                  mae = mean(abs(error)),
                  mean_cover = mean(observation*100),
                  quant_dist = mean(quant_dist))
qbmstats$model <- "QBM"
